---
title       : Pigeon Racing Results by Sex
subtitle    : Observing Differing Results by Color
author      : Ilana G.
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

### Pigeon racing is a very niche sport in the US

Hundreds of races occur every year, with each race being incredibly competitive. The races are monitored and tracked by the American Pigeon Racing Union (more information can be found here: http://www.pigeon.org/)

Races can be either short or long distances. In either case, however, pigeons can find themselves in dangerous situations, and are subject to the prey birds of North America. 

This app explores which birds are most successful at finishing one specific race. Data can be observed by pigeon gender, and additionally broken down by color. 

--- .class #id 

## Breakout by Pigeon Gender

```{r count, echo=FALSE}
#dataset <- read.csv("data/pigeon-racing.csv")
males <-subset(dataset, Sex == "C")
females <-subset(dataset, Sex == "H")
countMale <- nrow(males)
countFemale <- nrow(females)
meanMale <- mean(males$Speed)
meanFemale <- mean(females$Speed)
```

There are `r countMale` male pigeons in this dataset, and `r countFemale` female pigeons. The average speed for a male pigeon was `r meanMale` and the average speed for a female pigeon was `r meanFemale`. 

Because there are so few males in this particular race, gender is not a good measure for analysis. However, the lack of males could also indicate the training preference of the participants, or to some other reason why females are so heavily favored. 

--- .class #id 

## Breakout by Pigeon Color

When looking by color, there does not appear to be much deviation in average speed. 

```{r colorBreakdown, echo=TRUE}
#dataset <- read.csv("data/pigeon-racing.csv")
tapply(dataset$Speed, dataset$Color, mean)
```

--- .class #id 

## Ideas for Future Use

This app uses the data available from only one race. In the future, exploring the breakdown of finishers, speed, and place by location of race could provide more robust analysis.

In general, pigeon racing is something many people are not familiar with. Prior to beginning this project, I was unaware it existed. 


--- .class #id 

